---
title: "Skills of a Data Scientist"
author: "Team MMEC"
date: "October 21, 2018"
output: 
  rmdformats::readthedown:
    highlight: kate
---

## Motivation

Our motivation for this study is to gain an understanding of which skills are the most useful for a data scientist to have so that we can plan what courses to take in our Master's program.

## Approach

To answer this question scrape data scientist job listings on dice.com and extract the skills listed on the postings.

* 453 "Data Scientist" Job Postings
* Scrapped 15 October 2018

## Findings

### What Are The Key Skills?
```{r fig.width=10, fig.height=10, echo=FALSE, message=FALSE}
library(dplyr)
library(wordcloud)

#data <- read.csv("https://raw.githubusercontent.com/mikeasilva/data-scientist-skills/master/ds%20skills%20-%20cleaning%20-%20categorized_skills.csv", header = TRUE) %>%
data <- read.csv("ds skills - cleaning - categorized_skills.csv", header = TRUE) %>%
  filter(clean_skill != "Exclude") %>%
  filter(skill_group != "Position") %>%
  group_by(clean_skill, Period.Table.Group) %>%
  summarise(count = sum(count)) %>%
  arrange(-count) %>%
  ungroup()

set.seed(2)

wordcloud(words = data$clean_skill, freq = data$count, scale=c(8,.5),
          min.freq = 2, max.words=200, random.order=FALSE, rot.per=0, 
          colors=brewer.pal(8, "Dark2"))
```

### Top 20 Data Science Skills

```{r, echo=FALSE}
library(ggplot2)
data %>%
  top_n(20, count) %>%
  ggplot(.,aes(reorder(clean_skill, count), count)) + 
  geom_col(aes(fill = Period.Table.Group)) + 
  coord_flip() + 
  labs(x = NULL, y = "Count", title = "Data Science Skills", subtitle = "Mined from Job Listings") + 
  guides(fill=guide_legend(title=NULL, nrow=3, byrow=TRUE)) + 
  theme(legend.position="bottom")
```

## Limitations

* Data only for "Data Scientist" positions.  May have excluded data scientist positions under a different name.
* We only scrapped the skills portion of the job posting.  Additional skills could be found in the full job description section.

## Replication

See https://github.com/mikeasilva/data-scientist-skills