---
title: "Project 3 - Which are the Most Valued Data Science Skills?"
author: "Corey Arnouts, Mike Silva, Michael Yampol, Elizabeth Drikman"
date: "10/21/2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Overview

+ Motivation:

Our motivation for this study is to gain an understanding of which skills are the most useful for a data scientist to have so that we can plan what courses to take in our Master's program

+ Approach:

To answer this question we will scrape data scientist job listings on dice.com and extract the skills listed on the postings.

# Replication

+ System Requirements:

This study uses both R and Python 3. In order to replicate it you will need the following installed:

R:

- DBI
- RMySQL
- dplyr
- tidyr
- stringr
- splitstackshape
- Hmisc

# Replication Cont'd

Python 3:

- requests
- sqlalchemy
- pymysql
- beautifulsoup4
- selenium
- pandas

*You will need the Chrome selenium driver installed on your local machine*

Configuration:

- You will need to edit Credentials.R with your MySQL credentials

# Replication cont'd

+ Step 1: Setup.R

You will first need to run the Steup.R script. his will set up your local MySQL database. It will then launch a selenium controlled Chrome browser which will search for dice.com using "Data Scientist" as the keyword (in quotes).

+ Step 2: Dice_Scraper.py

The next step is to run the Dice Scraper script which will scrape all the URLs previously stored in the MySQL database. Note: You may need to run this more than once.

+ Step 3: Skills Miner.py

Next run the Skills Miner script which will create locations.csv, skills_counts.csv and skills_list.csv.

+ Step 4: Project_3_V2.R

Next run Project_3_V2.R which will clean up the skills_counts.csv and create data_science.csv

## Markdown Files

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

